### 2022-11-01 doc/src/VSLevel.tex
Fix mistakes in list of candidate interrupts for vstopi
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

\item
if \z{hstatus}.VGEIN is the valid number of a guest interrupt file,
bit~9 is one in both \z{vsip} and \z{vsie}, and \z{vstopei}
is not zero:
\begin{tightList}
\item[+]
a supervisor external interrupt (code~9) with the priority number
indicated by \z{vstopei};
\end{tightList}

\item
if \z{hstatus}.VGEIN is the valid number of a guest interrupt file,
bit~9 is one in both \z{vsip} and \z{vsie}, and \z{vstopei} is zero:
\begin{tightList}
\item[+]
a supervisor external interrupt (code~9) with priority number 256;
\end{tightList}

\item
if \z{hstatus}.VGEIN =~0, and \z{hvictl} fields IID =~9 and
$\mbox{IPRIO} \neq \mbox{0}$:
\begin{tightList}
\item[+]
a supervisor external interrupt (code~9) with priority number
\z{hvictl}.IPRIO;
\end{tightList}

@@

\begin{commentary}
When both \z{hstatus}.VGEIN =~0 and \z{hvictl}.VTI =~1, the
absence of an interrupt for VS level can be indicated only by setting
\z{hvictl} fields IID =~9 and IPRIO~=~0.
Software might want to use the pair IID =~9, IPRIO~=~0 generally to
represent\/ \emph{no interrupt} in \z{hvictl}.
\end{commentary}

>>>>

\item
if bit~9 is one in both \z{vsip} and \z{vsie}, \z{hstatus}.VGEIN is the
valid number of a guest interrupt file, and \z{vstopei} is not zero:
\begin{tightList}
\item[+]
a supervisor external interrupt (code~9) with the priority number
indicated by \z{vstopei};
\end{tightList}

\item
if bit~9 is one in both \z{vsip} and \z{vsie}, \z{hstatus}.VGEIN =~0,
and \z{hvictl} fields IID =~9 and $\mbox{IPRIO} \neq \mbox{0}$:
\begin{tightList}
\item[+]
a supervisor external interrupt (code~9) with priority number
\z{hvictl}.IPRIO;
\end{tightList}

\item
if bit~9 is one in both \z{vsip} and \z{vsie},
and neither of the first two cases applies:
\begin{tightList}
\item[+]
a supervisor external interrupt (code~9) with priority number 256;
\end{tightList}

@@

\begin{commentary}
When\/ \z{hvictl}.VTI =~1, the absence of an interrupt for VS level
can be indicated only by setting\/ \z{hvictl}.IID =~9.
Software might want to use the pair IID =~9, IPRIO~=~0 generally to
represent\/ \emph{no interrupt} in \z{hvictl}.
\end{commentary}
